Using Scipion for Stream Image Processing at Cryo-EM Facilities

### 2018-10-01 Review/answer_referee.tex

\point{The manuscript would benefit from a figure that outlines the layout of a typical Scipion system, showing computers, data connections, data flows in workflow scenarios, and how streaming is now implemented. At least for one of the three examples described, a figure would be helpful and make the manuscript more appealing to readers. }

\reply The following two figures have been included in the manuscript.

\begin{figure}
  \centering
      \includegraphics[width=0.75\textwidth]{images/diagram.pdf}
  \caption{Graphical representation of the data flow through the CNB facility. Green, blue and red lines represent the microscope private network, the \cnb local area network and the public network respectively.}
  \label{fig:cnbpipeline}

\end{figure}
\begin{figure}
%\hspace*{-2cm}                                                           
\includegraphics[width=1.0\textwidth]{images/scilifelab.pdf}
  \caption{Overview of the Session Wizard  developed at \scilifelab. A) The user triggers the wizard for any of the current microscopes. B) The wizard retrieves project information from the \textit{Application Portal} and reservation details from the \textit{Booking System}. C) The wizard creates data folders, executes the image copying script, configures the Scipion streaming project and logs the current session into a database. D) The \scipion project is used to generate on the fly web reports and invoice documents later on.}
  \label{fig:wizard}

@@

Using the HTTP header it is possible to guess the country in which \scipion has been installed. With these information we have created the usage map and table available at URL \url{http://scipion.i2pc.es/report_protocols/scipionUsage/} and  \url{http://scipion.i2pc.es/report_protocols/protocolTable/}. The data corresponds on ``global'' \scipion usage rather than ``facility'' usage but there 
is a one to one relationship between the  countries with highest number of \scipion projects and the countries with \scipion based EM facilities. The only exception to the rule is Canada where two of the original \scipion developers are setting up a new facility (McGill University).

Note that, in a effort to report real use and skip test projects, the number of projects in the map refers to the number of non empty \scipion projects updated more than once. That is, 
\scipion projects that have been opened in at least two different days. Another constraint is that developers' computers are filtered out.
\end{quote}

\point{Section 4 on Scipion setup at different facilities was confusing and unnecessarily lengthy. It wasn't clear to me if the "Additional software developments" made in 4.1.2 and 4.2.2 were general to Scipion or only made as a case-by-case scenario?}

\reply Section 4 has been extensively rewritten to take into account the reviewers' suggestions. In summary, we have included a two new images, delete several paragraphs, modify others and move those paragraphs related with future work to a different section.
